---
title: "math250_nov5_lata"
author: "Lata Bhatta"
format: html
editor: visual
embed-resources: true
---

```{r}
#| warning: false
#| message: false


library(tidyverse)
library(ISLR2)
library(palmerpenguins)

data("Carseats")

```

------------------------------------------------------------------------

**Question 1:**

Does this data provide evidence against the company's claim that the average price of their own seats is \$110?

```{r}
glimpse(Carseats)
mean(Carseats$Price)
```

The sample mean is about \$115.80, which is higher than the claimed \$110.

```{r}
ggplot(Carseats, aes(x = Price)) +
  geom_histogram(bins = 30, 
                 fill = "skyblue", 
                 color = "black") +
  geom_vline(xintercept = 110, 
             color = "red", 
             linetype = "dashed", 
             linewidth = 1)

```

$H_0: \mu = 110$ (the population mean price is \$110)

$H_a: \mu \ne 110$ (the population mean price is not \$110)

```{r}
t.test(Carseats$Price, mu = 110)


```

The p-value is small(1.429e-06), meaning data like ours would only occur about 0.01% of the time if the true mean was really \$110. This is strong evidence against the null hypothesis.

**Conclusion** We reject the null hypothesis and conclude that the true average price is not \$110. The actual average appears to be higher, around \$115.80.

**Question 2:**

Compute a level 90% confidence interval for the mean competitor price in the population from which this sample is drawn. What is the sample mean? What is the margin of error?

```{r}
mean(Carseats$CompPrice)

```

```{r}
t.test(Carseats$CompPrice, conf.level = 0.90)

```

Sample mean: \$124.97

90% Confidence Interval: (\$123.71 , \$126.23)

Margin of error: (126.23 - 123.71)/2 = \$1.26

We are 90% confident that the true population mean competitor price falls between \$123.71 and \$126.23. The margin of error is about \$1.26.

**Question 3:**

Create a table with counts of penguin species and home islands in the penguins set. Include marginal counts in your table.

```{r}
t<- table(penguins$species, penguins$island)
t
addmargins(t)

```

**Question 4:**
